---
title: "Weight of Fish"
author: "Ashley Saunders"
date: "`10/31/24"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```



## Perch
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottom",main="Adjusted R^2")
```

This demonstrates that the ideal model is Height and Width. The best models can be tested further.

### Best Models
```{r}
which.max(summary.out$adjr2)
```

The best model, according to the max codeblock, is number two. Its r-squared value is greater.

### Best Two regressor model
```{r}
summary.out$which[2,]
```

This data summary demonstrates that the model that incorporates H and W is the best model for perch fish. It has the greatest Adjusted r-squared value with two variables, indicating that it is the best two regression model.

## Pike
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

The model that incorporates all L1, L2, L3, H, and W seems to be the best one. However, the model that includes L1 and L3 seems to be the best two regressor model.

### Best Models
```{r}
which.max(summary.out$adjr2)
```

The optimal model is the one that incorporates all five variables.

### Best Two regressor model
We were able to concentrate its power on the corrected r-squared value by using leaps. Only the highest adjusted r-squared values for the first, second, third, fourth, and fifth variables for pike would then be provided. L1 and L3 are the best two regressors for the highest adjusted r-squared value, making them the top two regressor models, according to this type of jump analysis.

## Roach
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomleft",main="Adjusted R^2")
```

The model with two variables—L3 and W—seems to be the best one, making it the best two regressor model as well.

### Best Models

### Best Two regressor model

## Final Summary Statements